---
title: "Merge Habitat Restoration Projects with BMP-Treatment Type Projects"
author: "Jessica Henkel"
date: "July 19, 2017"
output: html_document
---

Load libraries:

```{r message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggmap)
library(lubridate)
library(geosphere)
library(stringi)

```{r warning = F, message = F, fig.width = 8, fig.height = 6}  
wat_tr <- 'data-raw/apdb_completed_categorized.csv'

# clean up stormwater data
watdat <- wat_tr %>% 
  read_csv %>% 
  select(Unique_Project_ID, ProjectLatitude, ProjectLongitude, Completion_Date, Project_Technology, Project_Activity) %>%
  rename(
    id = Unique_Project_ID,
    lat = ProjectLatitude, 
    lon = ProjectLongitude, 
    date = Completion_Date, 
    tech = Project_Technology, 
    type = Project_Activity
  ) %>% 
  mutate(
    id = stri_rand_strings(nrow(.), length = 4),
    lat = as.numeric(lat),
    lon = as.numeric(lon),
    date = as.numeric(date),
    tech = toupper(tech)
  ) %>% 
  filter(lat > 27.3 & lat < 28.2) %>% 
  filter(!is.na(date))

# water restoration station locs
watstat <- watdat %>% 
  mutate(id = stri_rand_strings(nrow(watdat), length = 4)) %>% 
  select(id, lat, lon) %>% 
  unique


# normalized water data
watdat <- watdat %>% 
  select(-lat, -lon)

save(watdat, file = 'data/watdat_JRH.RData', compress = 'xz')
save(watstat, file = 'data/watstat_JRH.RData', compress = 'xz')
```

Habitat restoration projects:
```{r}
## clean up habit restoration data
hab_tr <- 'data-raw/TBEP_Restoration Database_11_21_07_JRH.csv'
habdat1 <- hab_tr %>% 
   read_csv %>% 
  select(ProjectID, Latitude, Longitude, Project_Completion_Date, Project_Technology, Project_Activity) %>%
habdat<- rename(habdat1,
    id = ProjectID,
    lat = Latitude, 
    lon = Longitude, 
    date = Project_Completion_Date, 
    tech = Project_Technology, 
    type = Project_Activity) 
habdat2<- mutate(habdat,
    id = stri_rand_strings(nrow(habdat), length = 4),
    lat = as.numeric(lat),
    lon = as.numeric(lon),
    date = as.numeric(date),
    tech = toupper(tech)
  ) %>% 
  filter(lat > 27.3 & lat < 28.2) %>% 
  filter(!is.na(date))
  select(id, lat, lon) %>% 
  unique

# habitat restoration station locs
habstat <- habdat %>% 
  mutate(id = stri_rand_strings(nrow(habdat), length = 4)) %>% 
  select(id, lat, lon) %>% 
  unique

# normalized habitat data
habdat2 <- habdat2 %>% 
  select(-lat, -lon)

save(habdat2, file = 'data/habdat.RData', compress = 'xz')
save(habstat, file = 'data/habstat.RData', compress = 'xz')

all_projects<-(rbind(habdat2,watdat))

```{r}
head(habdat)
```
Locations of habitat restoration projects:
```{r}
head(habstat)
```