---
title: "Workflow Model through visNetwork"
author: "Kirsten Dorans <kdorans@mail.harvard.edu>"
date: "July 24, 2017"
output: html_document
---

# Based on Code from Ed Sherwood (visNetwork_Bayesian_Network_Template.Rmd)
# Also tried to create this using Katie's code Restoration_activities.Rmd (with Diagrammer package)
# 7.25.17 - put in 'archive folder', as used Diagrammer to create this figure (Diagrammer_WorkflowOverallDiagram.Rmd)

```{r setup, include=FALSE}
library(visNetwork)
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1. Develop a Simple Diagram to Illustrate the Simplified Worflow Diagram
  # First only WQ, Restoration --> Spatial Join
  # Not sure how to put WQ etc to left of Spatial join, see if adding more things helps
```{r}
nodes <- data.frame(id=1:3, 
                    label = c("Water Quality Data", "Restoration Data", "Spatial Join"), 
                    group = c("Dataset", "Dataset", "Process"),
                    level = c(1,3,2),
                    shape = c("square", "square", "circle"),
                    title = paste0("<p><b>", c("Water Quality Data", "Restoration Data", "Spatial Join"),"</b></p>"),
                    color = c("red", "red", "lightblue"),
                    shadow = c("true", "true", "true"))

# this is weird: # plot(nodes)

edges <- data.frame(from=c(1,2), to = c(3,3))
visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrows = "to") %>%
  visGroups(groupname = "Dataset", color = "red", shape = "square") %>%
  visGroups(groupname = "Spatial Join", color = "lightblue", shape = "circle") %>%
  visLegend(position = "right", main = "Legend") %>%
  visHierarchicalLayout()

```


## Part 2. Add Pre/Post Calc
```{r}
nodes <- data.frame(id=1:4, 
                    label = c("Water Quality Data", "Restoration Data", "Spatial Join", "Pre/Post Calculation"), 
                    group = c("Dataset", "Dataset", "Process", "Process"),
                    level = c(1,3,2,2),
                    shape = c("square", "square", "circle", "circle"),
                    title = paste0("<p><b>", c("Water Quality Data", "Restoration Data", "Spatial Join", "Pre/Post Calculation"),"</b></p>"),
                    color = c("red", "red", "lightblue", "lightblue"),
                    shadow = c("true", "true", "true", "true"))

# this is weird: # plot(nodes)

edges <- data.frame(from=c(1,2,3), to = c(3,3,4))
visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrows = "to") %>%
  visGroups(groupname = "Dataset", color = "red", shape = "square") %>%
  visGroups(groupname = "Spatial Join", color = "lightblue", shape = "circle") %>%
  visLegend(position = "right", main = "Legend") %>%
  visHierarchicalLayout()

```


## Part 3. Add BN Model, Interpretations
  # Works, but only saved low-res figure. To try to figure this out.
```{r}
nodes <- data.frame(id=1:6, 
                    label = c("Water Quality Data", "Restoration Data", "Spatial Join", "Pre/Post", "BN Model", "Interpret"), 
                    group = c("Dataset", "Dataset", "Process", "Process", "Process", "Process"),
                    level = c(1,3,2,2,2,2),
                    shape = c("square", "square", "circle", "circle", "circle", "circle"),
                    title = paste0("<p><b>", c("Water Quality Data", "Restoration Data", "Spatial Join", "Pre/Post Calculation", "BN Model", "Interpret"),"</b></p>"),
                    color = c("red", "red", "lightblue", "lightblue", "lightblue", "lightblue"),
                    shadow = c("true", "true", "true", "true", "true", "true"))

edges <- data.frame(from=c(1,2,3,4,5), to = c(3,3,4,5,6))
visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrows = "to") %>%
  visGroups(groupname = "Dataset", color = "red", shape = "square") %>%
  visGroups(groupname = "Spatial Join", color = "lightblue", shape = "circle") %>%
  visLegend(position = "right", main = "Legend") %>%
  visHierarchicalLayout()

```

